% \begin{abstract}

% Cameras attached to small quadrotor aircraft are rapidly becoming a ubiquitous tool for cinematographers, enabling dynamic camera movements through 3D environments.
% Currently, professionals use these cameras by flying quadrotors manually, a process which requires much skill and dexterity. 
% In this paper, we investigate the needs of quadrotor cinematographers, and build a tool to support video capture using quadrotor-based camera systems.
% We begin by conducting semi-structured interviews with professional photographers and videographers, from which we extract a set of design principles.
% We present a tool based on these principles for designing and autonomously executing quadrotor-based camera shots.
% Our tool enables users to: (1) specify shots visually using keyframes; (2) preview the resulting shots in a virtual environment; (3) precisely control the timing of shots using easing curves; and (4) capture the resulting shots in the real world with a single button click using commercially available quadrotors.
% We evaluate our tool in a user study with novice and expert cinematographers.
% We show that our tool makes it possible for novices and experts to design compelling and challenging shots, and capture them fully autonomously.

% \end{abstract}

\section{Abstract}

Cameras attached to small quadrotor aircraft are rapidly becoming a ubiquitous tool for cinematographers, enabling dynamic camera movements through 3D environments.
Currently, professionals use these cameras by flying quadrotors manually, a process which requires much skill and dexterity. 
In this paper, we investigate the needs of quadrotor cinematographers, and build a tool to support video capture using quadrotor-based camera systems.
We begin by conducting semi-structured interviews with professional photographers and videographers, from which we extract a set of design principles.
We present a tool based on these principles for designing and autonomously executing quadrotor-based camera shots.
Our tool enables users to: (1) specify shots visually using keyframes; (2) preview the resulting shots in a virtual environment; (3) precisely control the timing of shots using easing curves; and (4) capture the resulting shots in the real world with a single button click using commercially available quadrotors.
We evaluate our tool in a user study with novice and expert cinematographers.
We show that our tool makes it possible for novices and experts to design compelling and challenging shots, and capture them fully autonomously.
