\prefacesection{Acknowledgments}

This dissertation would have been impossible without the help and support of many people.
I am indebted to all of you, and I am delighted to take this opportunity to recognize the positive impact that all of you have had on my life.

I want to begin by thanking the world's greatest advisor, Pat Hanrahan.
You took me on as your student even though I didn't know what I was doing.
You were so patient with me, and you gave me the time I needed to grow into a good student and an independent researcher.
You gave me the freedom to choose my own research directions.
You spent countless hours with me discussing research ideas, and you provided a seemingly endless supply of helpful feedback on paper drafts and talks.
Your guidance and mentorship have been transformative.

I want to thank Fr{\'e}do Durand and Doug James for serving on my dissertation reading committee.
Fr{\'e}do's notes on writing became my bible during my graduate studies, and I especially appreciate the advice Doug gave me about choosing research problems back at Harvard.
Doug and Fr{\'e}do also provided very helpful and detailed feedback on an early version of my job talk. I want to thank Ron Fedkiw and Stephen Boyd for serving on my dissertation defense committee.
Ron's lab was an intellectual home-away-from-home, and I especially enjoyed all of our lively discussions over the years.
I also heard a rumor that Ron rescued my Stanford application from the reject pile -- thank you.
Stephen's textbooks, classes, online lectures, and office hours were always incredibly educational, both in their substance and style.

I want to thank Hanspeter Pfister.
You were the first person to give me a chance to do research outside my home town.
This opportunity changed my life.
I also want to thank John Owens.
You were the first person I ever met at an academic conference, and have been an exemplary role model and continuing source of inspiration ever since.
I especially appreciate your guidance on re-applying to Stanford, which undoubtedly changed my life for the better.
While you were hosting me for a visit at UC Davis, Shubho Sengupta offered a comfy couch to sleep on, and Andrew Davidson gave me a lift to the airport -- thank you.

I want to thank my recommenders:
Adam Finkelstein, Pat Hanrahan, Doug James, John Owens, Hanspeter Pfister, and Sudipta Sinha.
You all submitted a gazillion recommendation letters on my behalf, and were all so incredibly generous with your time.
Discussing research ideas with Adam was always fun and inspirational.
Sudipta introduced me to submodular functions, which had a big impact on this dissertation, and our whiteboard sessions were some of my favorite experiences in graduate school.

During my time at Stanford, I benefited from many other amazing mentors.
Floraine Berthouzoz was an incredible role model and collaborator.
Our discussions were always fun and inspirational, and our late-night paper editing sessions had a lasting impact on me.
I wish I could have shared more of the ideas in this dissertation with you.
Russ Tedrake carefully replied to so many of my emails, and his online lectures inspired much of the work in this dissertation.
Stefanie Jegelka's tutorials and online lectures also directly inspired the work in this dissertation.
Mykel Kochenderfer and Silvio Savarese agreed to participate in my qualifying exam -- thank you.
Vladlen Koltun and Ge Wang agreed to take me on as a rotation student even though I didn't know what I was doing.
Maneesh Agrawala, Michael Bernstein, Kayvon Fatahalian, Doug James, James Landay, and Mac Schwager provided valuable ongoing advice, and were all extremely generous with their time.
Wilmot Li provided detailed and helpful feedback on an early paper draft.
Working with John Owens and David Luebke at Udacity was a once-in-a-lifetime opportunity.
Working closely with Frank Dellaert at Skydio was incredibly fun and educational.
Debadeepta Dey, Neel Joshi, Ashish Kapoor, Shital Shah, and Sudipta Sinha at Microsoft Research were all fantastic collaborators.

I couldn't have asked for better friends, colleagues, and labmates at Stanford.
Niels Joubert immediately became a close collaborator and an even closer friend.
Indeed, many of the ideas in this dissertation were conceived during our memorable late-night coding sessions.
Anh Truong and Jane E quickly became trusted confidants and valued collaborators.
I especially appreciate all of Anh's fantastic work on our 3D scanning project, and Jane's work to narrate one of our supplementary videos.
Gilbert Bernstein, Zach DeVito, James Hegarty, Matt Fisher, Sharon Lin, Jonathan Ragan-Kelley, Daniel Ritchie, Manolis Savva, Lingfeng Yang, and Yi-Ting Yeh were fantastic colleagues and role models.
I especially want to thank Zach and Jonathan for putting up with it when I would sleep in their office -- you were doing me a bigger favor than you realize.
Ross Daly and Mackenzie Leake helped to prepare figures and supplementary materials for a paper at the last possible nanosecond.
Maxine Lim created several figures that appear in this dissertation.
Ali Alkhatib, Will Crichton, Abe Davis, Jingyi Li, Alex Poms, and Jerry Talton provided a ton of helpful feedback on various talks and paper drafts.
I especially appreciated all the conversations, coding sessions, and late-night snacks with Ed Quigley and Winnie Lin.
Justin Johnson was the world's greatest group project partner -- thank you for being so patient with me.
Enzo Busseti and Okke Schrijvers became life-long friends.

I also had the opportunity to work with many wonderful friends, colleagues, and labmates at Harvard.
Won-Ki Jeong was willing to work with me even though I didn't know what I was doing.
Bjoern Andres, Verena Kaynig-Fittkau, and Amelio Vazquez-Reina inspired me to learn everything I could about optimization.
Moritz Baecher, Kevin Dale, Kalyan Sunkavalli, and Justin Thaler became close friends.
I especially want to thank Kevin and Kalyan for generously sharing their accommodations at SIGGRAPH with me -- you were doing me a bigger favor than you realize.  
Johanna Beyer, Nicolas Bonneel, Michelle Borkin, Cris Cecka, Markus Hadwiger, Daniel Haehn, Ray Jones, Bobby Kasthuri, Seymour Knowles-Barley,  Jeff Lichtman, Miriah Meyer, Nicolas Pinto, and Amanda Randles were wonderful collaborators and role models.

I appreciate the technical and administrative support I received throughout my graduate studies.
Weichao Qiu provided extensive technical support with his incredibly useful UnrealCV Python library.
Jim Piavis and Ross Robinson provided valuable expertise as safety pilots, and Don Gillett granted us permission to 3D scan his barn.
I am also thankful for the support I received from the exceptional administrative staff in the Stanford Computer Science Department.
In particular, Helen Buendicho, Chris Downey, Jam Kiattinant, Andrea Kuduk, Jillian Lentz, Monica Niemiec, and Jay Subramanian have all gone out of their way to help me countless times.

The work in this dissertation was funded by NSERC and a generous grant from Google.
3DRobotics generously donated the drone hardware we used throughout this dissertation, and granted us permission to 3D scan their industrial scene.
Thank you.

Moving beyond academia, I am grateful for the people in my personal life that have helped and supported me throughout my graduate career.
In Calgary, Chelsea Leishman and the rest of Leishman family always believed in me.
Rob Faust remains a life-long friend, and is still the best DJ partner on the planet.
In Boston, Eric Baczuk and Simon Scheider were always great workout buddies, and I always enjoyed our endless conversations at Chipotle.
When I got to Stanford, I was fortunate to navigate the challenges and adventures of graduate student life alongside Okke Schrijvers.
Shannon Hoban and the rest of the Hoban family, Danielle Radin, Nikil and Tara Viswanathan, Ian Winters, and Brooke Wright all helped to make Stanford feel like home.
Dinner parties with Greg Benedict and Leah Meth were always welcome study breaks.
Cedar House in Berkeley was a home-away-from-home, and Iris Corey, Hannah Marshall, and Armin Samii immediately became close friends.
I especially appreciate Armin for hosting me when I was considering attending UC Berkeley for graduate school, and I want to thank Armin and Dave Jackson for lending me their spare hotel room at SIGGRAPH.

Throughout my graduate studies, I had the opportunity to meet many wonderful housemates.
In particular, Heather and Zac Altman, Katie Ballenger, Caroline Beaudon, Akhila Bettadapur, Nigel Kooreman, Felipe Pincheira, Jessica Schrouff, Gustavo Schwenkler, Alex and Andreas Zoellner quickly became close friends, and all made the Hackmann House a joy to come home to.
Living in the Facebook House was surreal and hilarious thanks to Kai Kuspa.
I was extremely fortunate to live in Hawthorne Manor with  Aladin Corhodzic, Mike D'Amico, Sherif Kassatly, and Ibrahim Toukan.
I experienced so many laughs and wonderful memories with all of you.
I especially appreciate Sherif and Ibrahim for lending me a couple of months of rent at one point -- thank you.
Sherif also did me a huge favor by lending me his old laptop when mine got stolen.

My time at Stanford was undoubtedly more fun because of all the opportunities I had to get in my musical happy place through DJing.
I am thankful for all my friends that made this possible.
Armin Samii hosted the best house party of all time, and trusted me to DJ at it.
Jack Wang at KZSU trusted me to DJ at Stanford football games soon after we met.
Jake Zeller went out of his way to connect me with nightclubs in San Francisco, which ultimately enabled me to open for the Chainsmokers.
Working with Ladidi Gharba was a once-in-a-lifetime opportunity.
I miss you.
Henrik Thorenfeldt trusted me to DJ at the Young Scandinavians Club cabin at Clear Lake.
We quickly became close friends, and Clear Lake became a second family.
Brian Mac immediately became a close friend and trusted DJ partner.

Finally, I want to thank my mom and dad, Judy and Rodger Roberts, for their kind words of support over the years.
And I especially want to thank my brother, Anthony Roberts.
Several times throughout my studies, you loaned me a significant amount of money, and these extraordinary acts of trust enabled me to continue pushing forward.
I would not have been able to complete this dissertation without you.
Thank you.
